---
title: "analysis"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidybayes)
library(latex2exp)
library(here)
library(brms)
source(here("R", "utils.R"))
theme_set(theme_minimal(base_size=12) + theme(legend.position = "top"))
```

```{r, message=FALSE}
fn_test_britta <- here("results", "pretests", "results-britta.csv")
data_test_britta <- read.csv(fn_test_britta, sep=",") %>% as_tibble()
selected_trials <- data_test_britta %>%
  filter(str_detect(trial_name, "image_selection")) %>% 
  pull(id) %>% unique()

subjects = c("gosia", "mingya", "charlotte", "pablo", "heiner", "ulrike")
data <- tibble()
for(subj in subjects) {
  fn <- here("results", "pretests", paste("results-", subj, ".csv", sep=""))
  if(subj %in% c("pablo", "vini")) { data_subj <- read.csv(fn, sep=",") %>% as_tibble() 
  } else { data_subj <- read.csv(fn, sep=";") %>% as_tibble()
  }
  data <- bind_rows(data, data_subj %>% add_column(submission_id = subj))
}
data <- data %>% group_by(submission_id) %>% 
    mutate(selected_pic = str_replace_all(selected_pic, "picture", "pic"), 
           expected = str_replace_all(expected, "picture", "pic")) %>% 
    mutate(selection = 
             factor(selected_pic, 
                    levels = c("pic1", "pic2", "pic3", 
                               "pic2_pic3", "pic1_pic2", "pic1_pic3",
                               "pic1_pic2_pic3"), 
                    labels = c("contrast", "single", "single", "both", 
                               "pic1_pic2", "pic1_pic3", "all"))) %>% 
  mutate(QUD = case_when(question == "cons" ~ "will-q", 
                         question == "if_ant" ~ "if-p",
                         question == "neutral" ~ "neutral", 
                         T ~ question)) %>% 
  mutate(id0 = str_replace(id0, "_horiz", ""),
         id1 = str_replace(id1, "_horiz", ""),
         id2 = str_replace(id2, "_horiz", "")) %>% 
  select(-question)
```

Sanity check data. Check that each participant has the same scenes in specific trials.

```{r}
N = data$submission_id %>% unique() %>% length()
df = data %>% 
  select(submission_id, id, type, picture1, picture2, picture3) %>% 
  distinct() 
df %>% group_by(id, type) %>% dplyr::count() %>% filter(n != N)

data %>% ungroup() %>% select(id, type, id0, id1, id2) %>% 
  group_by_all() %>% 
  dplyr::count() %>% filter(n != N)

```

Trials where a pragmatic and a literal selection is possible

```{r}
trials_lit_prag = c("trial8", "trial19", "trial20", "trial21", "trial24")
df <- data %>% filter(id %in% trials_lit_prag) %>% 
  dplyr::select(submission_id, selection, type, id)

# by trials
df %>% group_by(id) %>% 
  ggplot(aes(x=id, fill=selection)) + 
  geom_bar(stat="count", position=position_dodge())

# by subjects
df %>% 
  ggplot(aes(x=submission_id, fill=selection)) + 
  geom_bar(stat="count", position=position_dodge())
```

Practice trials

```{r}
practice_trials = c("trial7", "trial8", "trial11", "trial25")

df <- data %>% filter(id %in% practice_trials) %>% 
  dplyr::select(submission_id, selection, id)

df %>% ggplot(aes(x=id, fill=selection)) + 
  geom_bar(stat="count", position=position_dodge(preserve = 'single'))
```

Note: for Pablo there was a mistake in the code such that the attention-check
said to select a different picture than expected.

```{r}
df %>% filter(selection == "contrast")
```


Trials, where a selection of one is risky since no clue for neither of both
Trial11 is a practice trial, trial13 a filler trial.

```{r}
risk_trials = c("trial11", "trial13")

df <- data %>% filter(id %in% risk_trials) %>% 
  dplyr::select(submission_id, selection, id, type)

df %>% ggplot(aes(x=id, fill=selection)) + 
  geom_bar(stat="count", position=position_dodge())
```

## Attention-check for Prolific

Filter out participants who did not get attention checks right
Based on amoutn of points participants win during experiment:
100: single correct choice
50: 2 pictures selected, including the correct one
-100: 1 picure selecte, not including the correct one

```{r}
attention_checks = data %>% filter(type=="attention-check") %>% 
  dplyr::select(submission_id, id, type, selected_pic, expected, money, 
                timeSpent, comments, startDate) %>% 
  mutate(score = case_when(expected == selected_pic ~ 100,
                           str_detect(selected_pic, expected) ~ 50,
                            T ~ -100))

attention_checks.out = attention_checks %>%
  group_by(submission_id, timeSpent, comments, startDate) %>% 
  filter(score == -100)

attention_checks.out %>% ungroup() %>%
  dplyr::select(submission_id, id)

attention_checks.results = attention_checks %>%
  group_by(id, score) %>% dplyr::count() %>% 
  group_by(id) %>% mutate(ratio = n/sum(n)) %>% 
  mutate(score = factor(as.integer(score)))

attention_checks.results %>% ggplot(aes(x=id, y=ratio)) +
  geom_bar(stat="identity", position = position_dodge(), aes(fill=score))

attention_checks.results %>% ggplot(aes(x=id, y=n)) +
  geom_bar(stat="identity", position = position_dodge(), aes(fill=score))
```

all scores with -100 are from Pablo: there was a mistake, is fixed now.

```{r}
attention_checks %>% filter(id == "trial23" & score == 50) 
data %>% filter(submission_id == "mingya" & id == "trial23") %>% 
  dplyr::select(selected_pic, starts_with("property_id"))
```

Attention-check trial 23 is now slightly changed, such that there is a clear correct scene, 
that is, 2 contrast scenes and participants should select the single correct scene. Because people may do the experiment carefully, but overread 
the instruction in the attention-check '..so click on the picture in the middle'.


## Plot critical trials

```{r}
data.critical = data %>% filter(type=="critical") %>% 
   select(submission_id, id, type, QUD, response, selected_pic, id2, id3, RT) %>% 
  mutate(picPair=paste(id2, id3, sep=" & "),
         picPair.long = case_when(picPair == "if2_unn & if2_unu" ~ "D. withDistractor-external", 
                                   picPair == "if1_un & if2_unu" ~ "B. w/oDistractor-external",
                                   picPair == "if1_un & if1_uu" ~ "A. w/oDistractor-internal",
                                   picPair == "if2_unn & if1_uu" ~ "C. withDistractor-internal"),
         picPair.short = case_when(picPair == "if2_unn & if2_unu" ~ "D", 
                                   picPair == "if1_un & if2_unu" ~ "B",
                                   picPair == "if1_un & if1_uu" ~ "A",
                                   picPair == "if2_unn & if1_uu" ~ "C"))

# by QUD
data.critical %>% group_by(QUD, selected_pic) %>% 
  summarize(n=n(), .groups = "drop_last") %>% 
  mutate(ratio = n / sum(n)) %>% 
  ggplot(aes(fill=selected_pic, y=QUD, x=n)) + 
  geom_bar(stat="identity", position=position_dodge(preserve = 'single'))

# by trial
data.critical %>% group_by(picPair.long, QUD, selected_pic) %>% 
  summarize(n=n(), .groups = "drop_last") %>% 
  mutate(ratio = n / sum(n)) %>% 
  ggplot(aes(fill=selected_pic, y=QUD, x=n)) + 
  geom_bar(stat="identity", position=position_dodge(preserve = 'single')) +
  facet_wrap(~picPair.long, scales = "free")

```

# Reaction times

Look at reaction times split across all picture pairs

```{r}
critical.RT = data.critical %>% 
  dplyr::select(submission_id, id, QUD, RT, picPair, picPair.short, 
                selected_pic, id2, id3) %>%
  mutate(visual_diff = case_when(picPair.short == "B" | picPair.short == "C" ~ T, 
                                 T ~ F)) %>% 
  group_by(QUD, picPair.short) 
critical.RT_means = critical.RT %>% 
  summarize(mean_RT = mean(RT), .groups = "drop_last")

critical.RT_means %>% 
  ggplot(aes(x=mean_RT, y=picPair.short)) + 
  geom_bar(stat="identity") + 
  facet_wrap(~QUD)
```

```{r}
p.rt = critical.RT %>%
  ggplot(aes(x=log(RT), color=picPair.short)) + geom_density() 
p.rt
p.rt + facet_wrap(~QUD)
ggsave(here("results", "figs", "empiric-rts.pdf"), p.rt,
       width=7, height=4)
```


## Training data

Look at ratio of correct answers, do they increase with increasing trial numbers?

```{r}
data.train = data %>% filter(type=="training") %>%
  mutate(correct=case_when(expected == response ~ T, T ~ F)) %>% 
  dplyr::select(correct, id, trial_number)

# ratio correct per trial number (different order per participant)
train.correct.nb = data.train %>% group_by(trial_number) %>% 
  summarize(ratio_correct = mean(correct))
train.correct.nb %>% 
  ggplot(aes(x=trial_number, y=ratio_correct)) + 
  geom_bar(stat="identity") + 
  scale_x_continuous(breaks=seq(1, 7))

# ratio correct per trial id
train.correct.id = data.train %>% group_by(id) %>% 
  summarize(ratio_correct = mean(correct))
train.correct.id %>% 
  ggplot(aes(x=id, y=ratio_correct)) + 
  geom_bar(stat="identity") +
  theme(axis.text.x=element_text(angle=90))
```

