---
title: "Analysis Pilot CommunicationBlocks Experiment"
output:
  html_document:
    df_print: paged
---

```{r, packages, message=F}
library(here)
library(tidyverse)
library(dplyr)
options(dplyr.summarise.inform = FALSE)

source(here("R", "utils.R"))
theme_set(theme_bw(base_size=12) + theme(legend.position = "top"))
```

```{r, message=FALSE, warning=FALSE}
fn <- "results_67_communicationBlocks_BG_pilot.csv"
data <- read_csv(here("results", fn)) %>% as_tibble() %>%
  group_by(submission_id)
```

## Meta information about participants

```{r, meta, echo=FALSE}
data.meta <- data %>% distinct_at(vars(c(submission_id)), .keep_all = T) %>%
  mutate(education=as_factor(education), gender=as_factor(gender))

data.meta$gender %>% summary()
data.meta$education %>% summary()
print("age:")
data.meta$age %>% summary()
print("timeSpent:")
data.meta$timeSpent %>% summary()
```

## Reaction times

```{r, timespent, message=FALSE}
data.rt <- data %>% 
  select(expected, RT, id, question, trial_name, type, timeSpent, trial_number, 
         response)
data.rt %>%
  ggplot(aes(x=id, y=RT)) + 
  geom_jitter(aes(color=question), width=0.2, height=0) +
  geom_boxplot(outlier.shape=NA) +
  theme(axis.text.x=element_text(angle=90), legend.position = "right") +
  facet_wrap(~type, scales="free_x")
```

### Reaction Times per trial-type

```{r, message=FALSE, results=FALSE, echo=FALSE, warning=FALSE}
data.rt %>% 
  group_by(submission_id) %>%
  mutate(timeAll = timeSpent * 60,
         timeExperiment = (sum(RT) / 1000),
         timeInstructions = timeSpent - timeExperiment,
         timeTraining = (sum(RT[type=="training"]) / 1000),
         timeTesting = timeExperiment - timeTraining
         ) %>% 
  summarise(timeAll, timeTraining, timeTesting) %>% 
  unique()
# first digits before point are in seconds 
```

```{r}
train_times = configure(c("train_times")) %>% as_tibble() %>% 
  pivot_longer(cols=everything(), names_to="id", values_to="min")
data.rt.train = data.rt %>% 
  mutate(correct = response == expected) %>% 
  group_by(submission_id, id, trial_number, correct) %>%
  filter(type == "training") %>% 
  summarize(time_sec=sum(RT)/1000) %>% 
  arrange(submission_id, trial_number)

data.rt.train %>% mutate(submission_id = as.factor(submission_id)) %>% 
  ggplot(aes(x=id, y=time_sec)) + 
  geom_boxplot(outlier.shape=NA) + geom_jitter() +
  geom_point(data=train_times, aes(x=id, y=min), size=1.5, color='red')
```

```{r, include=FALSE, echo=FALSE}
left_join(data.rt.train, train_times, by="id") %>% 
  filter(time_sec < min)
```

Training time:
- Fast run took me **53 seconds** while waiting for the animations,
- Fast run without waiting for the animations took **32 seconds**
- Thorough (slow) run took **99 seconds**
- Thus, anyone **below ~50 seconds** time might not have fully watched the animations (or understood the training)

--> Only one person (ID 2234) took below 50 secs (49s) but it is so marginal, I think training times are fine.


Test Time:
- Fast run took me **185 seconds** while still reading all text
- Very fast run took **117 seconds** only browsing over the questions quickly and sometimes clicking sloppily
- Thorough (slow) run took **244 seconds**
- Thus, anything **below ~150 seconds** was not done thorough enough and the person might not have read the questions properly

--> Two people took below 130 seconds (ID 2243 = 148s and ID 2237 = 114s). It might be possible to be as fast as 114 seconds while still fulfilling the task but only if you are highly concentrated. 

### Training time vs. nb correct answers

```{r, relation-train-rt, warning=FALSE, message=FALSE}
train.time_total = data.rt %>% group_by(submission_id, type) %>% 
  mutate(correct = response == expected) %>% 
  summarize(time_sec = sum(RT)/1000, n_correct = sum(correct)) %>% 
  filter(type == "training")

train.time_total %>% 
  ggplot() + geom_point(aes(x=n_correct, y= time_sec)) +
  geom_hline(aes(yintercept=train.time_total$time_sec %>% mean()), color='red') +
  geom_hline(aes(yintercept=train.time_total$time_sec %>% median()), color='blue')


```

### Reaction times per train trial for correct/wrong trials

```{r}
data.rt.train %>%
  ggplot(aes(y=id, x=time_sec, color=correct)) +
  geom_jitter(height=0.2, width=0) +
  geom_boxplot(outlier.shape=NA) +
  labs(x="Reaction time in seconds", y = "training id") 
```


## General comments all participants

```{r}
data %>% select(comments) %>%  filter(!is.na(comments) & comments!="") %>% 
  distinct()
```

## Training Trials

```{r}
data.train = data %>% filter(type=="training") %>%
  mutate(correct=case_when(expected == response ~ T, T ~ F))

# ratio correct per trial number (different order per participant)
train.correct.nb = data.train %>% group_by(trial_number) %>% 
  summarize(ratio_correct = mean(correct))
train.correct.nb %>% 
  ggplot(aes(x=trial_number, y=ratio_correct)) + 
  geom_bar(stat="identity") + 
  scale_x_continuous(breaks=seq(1, 7))

# ratio correct per trial id
train.correct.id = data.train %>% group_by(id) %>% 
  summarize(ratio_correct = mean(correct))
train.correct.id %>% 
  ggplot(aes(x=id, y=ratio_correct)) + 
  geom_bar(stat="identity") +
  theme(axis.text.x=element_text(angle=90))
```

## Example Test-Trial

```{r, warning=FALSE}
data.example_test = data %>% filter(type=="test-example") %>%
  group_by(submission_id) %>% 
  dplyr::select(expected, selected_pic) %>% 
  transmute(correct = expected == selected_pic)

rate_correct_example = data.example_test %>%
  summarize(ratio_correct = sum(correct) / n()) %>% 
  pull(ratio_correct)

ids.wrong = data.example_test %>% filter(!correct) %>% pull(submission_id) %>% 
  unique()
ids.wrong
```


## Test trials

Look at control test trials

```{r, message=FALSE}
data.control = data %>% filter(startsWith(type,"control")) %>% 
  mutate(correct = expected == selected_pic) %>% 
  group_by(id, type) %>%
  mutate(n=n(), n_correct = sum(correct), ratio_correct = n_correct/n) %>% 
  dplyr::select(c(id, type, n, n_correct, ratio_correct)) %>%
  distinct_at(vars(c(id, type)), .keep_all = T)
    
data.control %>% 
  ggplot(aes(x=ratio_correct, y=id)) + 
  geom_bar(aes(fill=type), stat="identity") +
  labs(x="ratio correct", title="control test trials", y="")
```

Clean data

```{r}
n_all = data$submission_id %>% unique() %>% length
data.cleaned = clean_data(data)
#from training trials:
data.cleaned <- data.cleaned %>% filter(!submission_id %in% c(2233, 2237))
n_kept = data.cleaned$submission_id %>% unique() %>% length

ratio_kept = round(n_kept/n_all, 2)
```

Data from `r ratio_kept` of all participants is retained.

## Plot critical trials

```{r, data-critical, echo=FALSE}
data.critical = data.cleaned %>% 
  filter(type=="critical") %>% 
  select(submission_id, id, type, question, response, expected, id1, id2,
         selected_pic) %>% 
  mutate(expectation = case_when(expected == "none" ~ FALSE,
                                 TRUE ~ TRUE)) %>%
  group_by(id1, id2)

data.critical$pic_combi = data.critical %>% group_indices()
data.critical <- data.critical %>% 
  mutate(pic_combi=paste(id1, id2, sep=" & ")) %>% 
  group_by(pic_combi, question) %>% mutate(n=n()) 

data.critical.rate = data.critical %>% group_by(question) %>% 
  summarize(rate_exhaustive = sum(response == "exhaustive") / n(),
            .groups = "drop_last") 
data.critical.rate.pic_combi = data.critical %>% 
  group_by(question, pic_combi) %>% 
  summarize(rate_exhaustive = sum(response == "exhaustive") / n(),
            .groups="drop_last") 
```

### Trials we make predictions about

1. across all different instantiations, i.e. exhaustive/non-exhaustive 
picture combinations

```{r}
conditions = configure(c("conditions"))
data.critical %>%
  ggplot(aes(fill=response, y=question)) + 
  geom_bar(position=position_dodge(preserve = 'single')) + 
  scale_y_discrete(breaks=names(conditions), labels = conditions) + 
  labs(y="Ann's question")

# same plot with exhaustive-picture selection ratios instead of absolute numbers
data.critical.rate %>%
  ggplot(aes(x=rate_exhaustive, y=question)) + 
  geom_bar(stat="identity") + 
  geom_text(aes(label=round(rate_exhaustive, 2)), hjust=1, color='white') +
  scale_y_discrete(breaks=names(conditions), labels = conditions) + 
  labs(y="Ann's question", x="selection rate exhaustive picture")
```

2. split among different instantiations of critical trials 
(i.e., across different picture combinations)

```{r}
data.critical.rate.pic_combi %>% 
  ggplot(aes(x=rate_exhaustive, y=question)) + 
  geom_bar(stat="identity") + 
  geom_text(aes(label=round(rate_exhaustive, 2)), hjust=1, color='white') +
  facet_wrap(~pic_combi)
```

